---
title: 'Submitted data error checks'
output: 
  html_document:
    toc: true
---

# 0. Instructions for submitters
Submitters should use this file to check for problems with submitted data.
Each of these html files contains a summary of the data in a single submitted spreadsheet file.
The html name is based on the name of the submitted file.
Use the details below to check:

* Institute abbreviation, submitter and contributor names
* The plot location(s), using the map zoom and pan features if needed
* For problems in the first sections; "OK" means there are no problems in a particular section, "warning" is something that should be checked (but might be OK), "error" is a problem that needs to be addressed
* For numeric values outside the expected range in the "Value checks" section
* Variables with missing values--are there any missing that you thought you included?
* Plots of flux, cumulative emission over time, and final cumulative emission for strange patterns, unexpectedly high or low values
* Plots of weather data for appropriate differences between plots and expected diurnal or other patterns
* Plots of manure and application data for correct values

Finally, the numeric summary at the end might provide details that can help in pinpointing problems, but typically does not need to be checked.

# 1. Submitter
```{r, echo = FALSE}
kable(dat[[i]][[j]]$submitter[, -1], row.names = FALSE)
```

# 2. Contributors
```{r, echo = FALSE}
kable(dat[[i]][[j]]$contrib, row.names = FALSE)
```
# 3. File and directory names
```{r, echo = FALSE}
print(i)
print(j)
```

# 4. Location
```{r, echo = FALSE}
library( leaflet )
library( magrittr )
```

```{r, echo = FALSE}
plots <- dat[[i]][[j]]$plots
ll <- unique(plots[, c('lat', 'long')])

subscr <- data.frame(lat=c(ll$lat),
                    lon=c(ll$long))

leaflet() %>% addTiles() %>% 
  addCircleMarkers(data = subscr,
                   lat = ~lat, lng = ~lon,
                   color = "blue")

```

# 5.Keys and codes 
```{r, echo = FALSE}
exper <- dat[[i]][[j]]$exper
treat <- dat[[i]][[j]]$treat
emis <- dat[[i]][[j]]$emis
pubs <- dat[[i]][[j]]$pubs
```

## Codes in Treatments sheet
```{r, echo = FALSE}
if (all(exper$exper %in% treat$exper)) {
  cat('OK\n')
} else {
  print('Missing experiment codes in Treatments sheet.')
}

if (all(treat$exper %in% exper$exper)) {
  cat('OK\n')
} else {
  print('Missing experiment codes in Experiments sheet.')
}
```

## Codes in Plots sheet
```{r, echo = FALSE}
if (all(exper$exper %in% plots$exper)) {
  cat('OK\n')
} else {
  print('Missing experiment codes in Plots sheet.')
}

if (all(plots$exper %in% exper$exper)) {
  cat('OK\n')
} else {
  print('Missing experiment codes in Experiments sheet.')
}
```

## Codes in Emission sheet
```{r, echo = FALSE}
if (all(exper$exper %in% emis$exper)) {
  cat('OK\n')
} else {
  print('Missing experiment codes in Emission sheet.')
}

if (all(emis$exper %in% exper$exper)) {
  cat('OK\n')
} else {
  print('Missing experiment codes in Experiments sheet.')
}
```

## Code merge check (matching project, experiment, field, plot, treatment)
```{r, echo = FALSE}
m1 <- merge(exper, treat, all = TRUE)
m2 <- merge(m1, emis, all = TRUE)

if (nrow(m1) == nrow(treat)) {
  cat('OK\n')
} else {
  print('Merge problem 1')
  print(intersect(names(exper), names(treat)))
}

if (sum(is.na(c(m1$proj, m1$exper, m1$treat))) == 0) {
  cat('OK\n')
} else {
  print('Merge problem 2')
}

if (nrow(m1) == max(nrow(treat), nrow(exper))) {
  cat('OK\n')
} else {
  print('Merge problem 3')
}

if (sum(is.na(c(m2$proj, m2$exper, m2$treat, m2$field, m2$plot))) == 0) {
  cat('OK\n')
} else {
  print('Merge problem 4')
  md <- m2[is.na(m2$proj) | is.na(m2$exper) | is.na(m2$field) | is.na(m2$plot), c('row.in.file.plot', 'row.in.file.int', 'proj', 'exper', 'pub.id', 'treat', 'field', 'plot')]
  md <- unique(md)
  print(md)
  #unique(emis[, c('proj', 'exper', 'pub.id', 'treat', 'field', 'plot')])
  #intersect(names(m1), names(emis))
}

if (nrow(m2) == nrow(emis)) {
  cat('OK\n')
} else {
  print('Merge problem 5')
  print('Some unmatched codes/names present')
  print('First 5 rows after merge:')
  print(m2[1:5, c('row.in.file.plot', 'row.in.file.int', 'proj', 'exper', 'pub.id', 'treat', 'field', 'plot')])
  stop('Merge problem 2, see error_check.Rmd')
}

#if (sum(is.na(c(m3$proj, m3$exper, m3$treat, m3$field, m3$plot))) == 0) {
#  cat('OK\n')
#} else {
#  print('Merge problem 6')
#  md <- m3[any(is.na(m3$proj), is.na(m3$exper), is.na(m3$treat), is.na(m3$field), is.na(m3$plot)), c('row.in.file.plot', 'row.in.file.int', 'proj', 'exper', 'treat', 'field', 'plot')]
#  md <- unique(md)
#  print(paste('Problems in', nrow(md), 'rows.'))
#  print('First 10 rows:')
#  print(md[1:min(10, nrow(md)), ])
#}

```

# 6. Publication info
## Check for missing codes
```{r, echo = FALSE}
if (all(exper$pub.id %in% pubs$pub.id)) {
  cat('OK\n') 
} else {
  print('Missing pub codes in Publications sheet.')
}
```

```{r, echo = FALSE}
if (all(pubs$pub.id %in% exper$pub.id)) {
  cat('OK\n') 
} else {
  print('Some pub codes missing in Experiments sheet.')
}
```

## Complete citations given
```{r, echo = FALSE}
if (all(grepl('[Dd][Oo][Ii]', pubs$citation))) {
  cat('OK\n') 
} else {
  print('DOI missing from Publications sheet.')
}
```

```{r, echo = FALSE}
if (all(nchar(pubs$citation) > 10)) {
  cat('OK\n') 
} else {
  print('Citation details missing from Publications sheet.')
}
```

# 7. Emission sheet

```{r, echo = FALSE}
d <- dat[[i]][[j]]$emis
# Add first row in file info by plot
xx <- d[d$interval == 1, c('cpmid', 'row.in.file.int', 'row.in.file.plot')]
names(xx)[2:3] <- c('first.row.int', 'row.plot')
d <- merge(d, xx, by = 'cpmid')
```

## Duplicated intervals
```{r, echo = FALSE}
s <- ddply(d, 'cpmid', summarise, n.int.duplicates = sum(duplicated(interval)))
x <- subset(s, n.int.duplicates > 1)
if (nrow(x) > 0) {
  y <- subset(d, cpmid == x$cpmid)
  print('Some intervals duplicated:')
  print(y[, c('file', 'institute', 'row.in.file.int', 'plot', 'rep')])
} else {
  cat('OK\n')
}
```

## Missing incorporation time

```{r, echo = FALSE}
x <- subset(d, incorp %in% c('deep', 'shallow') & is.na(time.incorp))
if (nrow(x) > 0) {
  print('Some problems')
  print(unique(as.character(x$file)))
  print(x[, c('file','row.in.file.int','institute')])
  print(table(d$incorp, d$time.incorp, exclude = NULL))
} else {
  cat('OK\n')
}

```

## Delay after application
```{r,echo=FALSE}
if (all(is.na(d$bta))) {
  cat('bta (cum. time since application began) is not available.\n')
} else if (min(na.omit(d$bta)) < 1) {
  cat('OK\n')
} else {
  cat('Warning: 1 hour or longer delay after starting application\n')
  cat('  bta = elapsed (cumulative) time since manure application *began*\n  ct = elapsed time of measurements\n  cta = elapsed time since application ended\n')
  cat('  First 10 rows\n')
  kable(d[1:10, c('row.in.file.int', 'app.start', 't.start', 'bta', 'ct', 'cta')])
}
```

## Missing or double interval number
```{r,echo=FALSE}
for (ii in unique(emis$cpmid)) {
  #cat(ii)
  dd <- emis[emis$cpmid == ii, ]
  if (all(diff(dd$interval) == 1)) {
    cat('OK\n')
  } else {
    print('Problem, see following rows')
    print(dd$row.in.file.int[ii <- which(diff(dd$int) != 1)])
    print(dd[sort(unique(c(ii, ii-1, ii+1))), c('row.in.file.int', 'plot', 'interval', 't.start')])
  }
}
```

## Missing time between intervals
```{r,echo=FALSE}
for (ii in unique(emis$cpmid)) {
  dd <- emis[emis$cpmid == ii, ]
  if (all(is.na(dd$t.start)) | all(is.na(dd$t.end))) {
    print('No start or end times provided, so cannot check for missing time.')
  } else if (all(dd$t.start[-1] == dd$t.end[-nrow(dd)])) {
    cat('OK\n')
  } else {
    print('Problem, see following rows (compare start time to end time in previous rows):')
    ii <- which(c(FALSE, dd$t.start[-1] != dd$t.end[-nrow(dd)]))
    print(dd$row.in.file.int[ii])
    #print(dd[ii + -2:2, c('row.in.file.int', 'plot', 'interval', 't.start', 't.end')])
  }
}
```
# 7. Value checks
Check to see if submitted values are within a reasonable range.

## Weather
```{r, echo = FALSE}
lim <- data.frame(vari = c('wind', 'rain.rate', 'air.temp', 'soil.temp', 'soil.temp.surf', 'air.temp.z', 'wind.z'),
                  lwr = c(0, 0, -10, -10, -10, 0, 0),
                  upr = c(20, 20, 40, 40, 40, 10, 10))

for (k in lim$vari) {
  cat(k, ': ')
  vv <- na.omit(d[, k])
  if (length(vv) > 0) {
    if (all(vv >= lim[lim$vari == k, 'lwr'] & vv <= lim[lim$vari == k, 'upr'])) {
      cat('OK\n')
    } else {
      cat('Some values out of range\n')
      cat('Limits: ')
      print(lim[lim$vari == k,])
      cat('Range: ')
      print(range(vv))
      cat('Value table:\n')
      print(table(vv, exclude = NULL))
      cat('Missing values: ', sum(is.na(vv)),'\n')
    }
  } else {
    cat('No values to check.\n')
  }
}
```

## Manure and application
```{r, echo = FALSE}
lim <- data.frame(vari = c('man.stor', 'man.dm', 'man.vs', 'man.tkn', 'man.tan', 'man.tic', 'man.ua', 'man.vfa', 'man.ph', 'app.rate', 'crop.z'),
                  lwr = c(0, 0.1, 0.1, 0.1, 0.1, 0.1, 0.1, 0, 4, 1, 0),
                  upr = c(600, 20, 20, 10, 10, 10, 10, 20, 9.5, 200, 50))

for (k in lim$vari) {
  cat(k, ': ')
  vv <- na.omit(d[, k])
  if (length(vv) > 0) {
    if (all(vv >= lim[lim$vari == k, 'lwr'] & vv <= lim[lim$vari == k, 'upr'])) {
      cat('OK\n')
    } else {
      cat('Some values out of range\n')
      print(range(vv))
    }
  } else {
    cat('No values to check.\n')
  }
}
```

## Emission
```{r, echo = FALSE}
lim <- data.frame(vari = c('j.NH3', 'e.int', 'e.rel'),
                  lwr = c(-3, -30, -5),
                  upr = c(60, 200, 1.1))

for (k in lim$vari) {
  cat(k, ': ')
  vv <- na.omit(d[, k])
  if (length(vv) > 0) {
    if (all(vv >= lim[lim$vari == k, 'lwr'] & vv <= lim[lim$vari == k, 'upr'])) {
      cat('OK\n')
    } else {
      cat('Some values out of range\n')
      print(range(vv))
    }
  } else {
    cat('No values to check.\n')
  }
}
```

# 8. Missing values
Check for missing values.

## All variables
```{r,echo = FALSE}
miss <- apply(d, 2, function(x) sum(is.na(x)))
miss <- miss[miss > 0]
if (length(miss) > 0) {
  cat('Some values missing:\n')
  cat('Table below has number of missing observations by variable:\n')
  print(miss)
} else {
  cat('OK, no values missing\n')
}
```

## Application method and measurement method
```{r, echo=FALSE}
if (any(is.na(plots$app.method))) {
  print('Missing app.method in some rows')
} else {
  cat('OK\n')
}
```
```{r, echo=FALSE}
if (any(is.na(plots$meas.tech))) {
  print('Missing measurement method in some rows')
} else {
  cat('OK\n')
}
```

# 9. Plots
## Calculated cumulative emission
Cumulative emission.
Missing values imputed (linear interpolation).

```{r, echo=FALSE}
d$first.rows <- factor(paste('Plots', d$row.plot, 'Emis.', d$first.row))

ggplot(d, aes(ct, e.rel, colour = first.rows)) + geom_line() + geom_point() + theme(legend.position = 'none') + facet_wrap(~ first.rows) + labs(x = 'Elapsed time (h)', y = 'NH3 emission (frac. app. TAN)', colour = 'Rows in file')
ggplot(d, aes(ct, e.rel, colour = first.rows)) + geom_line() + geom_point() + theme(legend.position = 'top') + labs(x = 'Elapsed time (h)', y = 'NH3 emission (frac. app. TAN)', colour = 'Rows in file')

if (!(all(is.na(d$cta)))) {
  ggplot(d, aes(cta, e.rel, colour = first.rows)) + geom_line() + geom_point() + theme(legend.position = 'top') + labs(x = 'Elapsed time (after application) (h)', y = 'NH3 emission (frac. app. TAN)', colour = 'Rows in file')
}

if (!(all(is.na(d$t.end)))) {
  ggplot(d, aes(t.end, e.rel, colour = first.rows)) + geom_line() + geom_point() + theme(legend.position = 'none') + labs(x = 'Date/time', y = 'NH3 emission (frac. app. TAN)', colour = 'Rows in file')
  ggplot(d, aes(t.end, e.rel, colour = first.rows)) + geom_line() + geom_point() + theme(legend.position = 'none') + facet_wrap(~ first.rows) + labs(x = 'Date/time', y = 'NH3 emission (frac. app. TAN)', colour = 'Rows in file')
}
```

## Final cumulative emission

```{r, echo = FALSE}
ggplot(plots, aes(e.rel.final, fill = treat)) + geom_histogram() + facet_grid(meas.tech ~ .) + labs(x = 'Final cum. emission (frac. app. TAN)')
```

## Relative versus absolute emission

```{r, echo = FALSE}
ggplot(plots, aes(e.rel.final, e.final)) + geom_point() + facet_grid(meas.tech ~ .) + labs(x = 'Final cum. emission (frac. app. TAN)', y = 'Final cum. emission (kg N/ha)')
```

## Flux

```{r, echo = FALSE}
ggplot(d, aes(ct, j.NH3, colour = first.rows)) + geom_step() + geom_point() + theme(legend.position = 'none') + facet_wrap(~ first.rows) + labs(x = 'Elapsed time (h)', y = 'NH3 flux (kg N/ha-h)', colour = 'Rows in file')
ggplot(d, aes(ct, j.NH3, colour = first.rows)) + geom_step() + geom_point() + theme(legend.position = 'top') + labs(x = 'Elapsed time (h)', y = 'NH3 flux (kg N/ha-h)', colour = 'Rows in file') 
if (!(all(is.na(d$cta)))) {
  ggplot(d, aes(cta, j.NH3, colour = first.rows)) + geom_step() + geom_point() + theme(legend.position = 'top') + labs(x = 'Elapsed time (from application) (h)', y = 'NH3 flux (kg N/ha-h)', colour = 'Rows in file')
}
```

## Weather data

```{r, echo=FALSE}
ggplot(d, aes(ct, wind, colour = first.rows)) + geom_line() + geom_point() + theme(legend.position = 'top') + labs(x = 'Elapsed time (h)', y = 'Wind (m/s', colour = 'Rows in file')
ggplot(d, aes(ct, air.temp, colour = first.rows)) + geom_line() + geom_point() + theme(legend.position = 'none') + labs(x = 'Elapsed time (h)', y = 'Air temp. (deg. C)', colour = 'Rows in file')
ggplot(d, aes(ct, rain.rate, colour = first.rows)) + geom_line() + geom_point() + theme(legend.position = 'none') + labs(x = 'Elapsed time (h)', y = 'Rain (mm/h)', colour = 'Rows in file')
ggplot(d, aes(ct, rain.cum, colour = first.rows)) + geom_line() + geom_point() + theme(legend.position = 'none') + labs(x = 'Elapsed time (h)', y = 'Rain (mm)', colour = 'Rows in file')
```

## Manure and application

```{r, echo = FALSE}
if (nrow(plots) < 5) {
  kable(plots[, c('institute', 'proj', 'exper', 'field', 'plot', 'man.dm', 'man.ph', 'man.tan', 'app.rate', 'tan.app')])
} else {
  ggplot(plots, aes(row.in.file.plot, man.dm)) + geom_point() + facet_grid(meas.tech ~ .) + labs(x = 'Row in Plot sheet', y = 'Manure DM (%)')
  ggplot(plots, aes(row.in.file.plot, man.ph)) + geom_point() + facet_grid(meas.tech ~ .) + labs(x = 'Row in Plot sheet', y = 'Manure pH')
  ggplot(plots, aes(row.in.file.plot, man.tan)) + geom_point() + facet_grid(meas.tech ~ .) + labs(x = 'Row in Plot sheet', y = 'Manure TAN (g/kg)')
  ggplot(plots, aes(row.in.file.plot, app.rate)) + geom_point() + facet_grid(meas.tech ~ .) + labs(x = 'Row in Plot sheet', y = 'Manure application (t/ha)')
  ggplot(plots, aes(row.in.file.plot, tan.app)) + geom_point() + facet_grid(meas.tech ~ .) + labs(x = 'Row in Plot sheet', y = 'TAN application (kg/ha)')
}
```

# 10. `dfsumm` summary 
```{r, echo=FALSE}
print(dfsumm(d))
```

