---
title: 'Header check for ALFAM2 data'
output: pdf_document
author: Sasha D. Hafner
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

# Summary
Checks that all column headers in the data files are described in the files in the headers directory. 

# Header check

```{r}
ihead <- read.csv('../../headers/interval-level_variables.csv')
phead <- read.csv('../../headers/plot-level_variables.csv')
```

```{r}
idat <- data.table::fread('../../data-output/03/ALFAM2_interval.csv.gz')
pdat <- data.table::fread('../../data-output/03/ALFAM2_plot.csv.gz')
```

Variables `e.6` and similar are described as `e.x` in the description columns in the rows for `e.6` etc.
Here, drop them.

```{r}
names(pdat) <- gsub('\\.[0-9]+$', '\\.(time)', names(pdat))
phead$Name <- gsub('\\.[0-9]+$', '\\.(time)', phead$Name)
```

Missing in plot-level header file.
```{r}
unique(names(pdat))[!unique(names(pdat)) %in% phead$Name]
```

If results is `character(0`, none are missing.

No longer used--remove from plot-level header file.
```{r}
phead$Name[!phead$Name %in% names(pdat)]
```

Missing in interval-level header file.
```{r}
names(idat)[!names(idat) %in% ihead$Name]
```

No longer used--remove from interval-level header file.
```{r}
ihead$Name[!ihead$Name %in% names(idat)]
```




